\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Cite for Tor Browser 5.0.3.
Move the environments into the section on eval criteria.
This may not be the best place for it, but I feel it needs a place
outside of the section on Study 1, as it belongs equally to Study 1 and
Study 2.

All our experiments use (modified versions of)
Tor Browser~5.0.3, which was the current stable release at the time we began.
Though there were new releases during the course of the experiments,
we stuck with 5.0.3 so as not to introduce potential confounding factors.

\subsection{Censorship Environments}
\label{sec:environments}
We simulated three censorship environments,
which we labeled ``E1,'' ``E2,'' and ``E3''
in order of increasing severity.
We designed the environments to be representative
of what, in our estimation, are important real-world
cases of censorship, but they are not intended to imitate
any particular country's censorship exactly.

@@

>>>>

\subsection{Censorship Environments}
\label{sec:environments}
In each experiment, we simulated three censorship environments,
which we labeled ``E1,'' ``E2,'' and ``E3''
in order of increasing severity.
We designed the environments to be representative
of what, in our estimation, are important real-world
cases of censorship, but they are not intended to imitate
any particular country's censorship exactly.

@@

All our experiments use (modified versions of)
Tor Browser~5.0.3, which was the current stable release at the time we began~\cite{torbrowser-503}.
Though there were new releases during the course of the experiments,
we stuck with 5.0.3 so as not to introduce potential confounding factors.
